Thomas et al. 2025

### 2025-01-09 AT_2025.qmd
Continuing minor updates

---
title: "Alix Thomas, PA & PE lipid interactomics"
format: 
  html:
    embed-resources: true
standalone: true
---

@@

**Authors:**

@@

**Journal, issue, CRBN:** Chemical Communications

**DOI:** <https://doi.org/10.1039/D4CC03599B>

@@

Phosphatidylethanolamine (PE) is a ubiquitous lipid species in higher eukaryotes which resides preferentially in mitochondria. Here, we synthesized a multifunctionalized PE derivative (1) de-signed to identify PE-binding proteins in intact cells through photo-crosslinking and subsequent isolation and proteomic analysis of the PE-protein conjugates. Due to its aromatic caging group, 1 is initial-ly concentrating in perinuclear membranes. After uncaging, rapid translocation to mitochondria was observed. Hence, the tool is useful for tracking PE location and for determining the PE interac-tome. A trifunctional phosphatidic acid (PA) derivative in compari-son was rapidly metabolized and is hence more limited in its use.

>>>>

---
title: "Thomas et al. 2025"
format: 
  html:
    embed-resources: true
standalone: true
---

@@

**Title:** Trifunctional lipid derivatives: PE’s mitochondrial interactome

**Authors:** Alix Thomas, Rainer Mueller, Ana Kojic, Scotland E. Farley, Frank Stein, Per Haberkant, Carsten Schultz*

(* corresponding: <schulcar@ohsu.edu>{target="_blank"})

@@

**Journal, ISSN:** Chemical Communications, 1359-7345, 1364-548X

**DOI:** <https://doi.org/10.1039/D4CC03599B>{target="_blank"}

@@

Phosphatidylethanolamine (PE) is a ubiquitous lipid species in higher eukaryotes which resides preferentially in mitochondria. Here, we synthesized a multifunctionalized PE derivative (1) de-signed to identify PE-binding proteins in intact cells through photo-crosslinking and subsequent isolation and proteomic analysis of the PE-protein conjugates. Due to its aromatic caging group, 1 is initially concentrating in perinuclear membranes. After uncaging, rapid translocation to mitochondria was observed. Hence, the tool is useful for tracking PE location and for determining the PE interactome. A trifunctional phosphatidic acid (PA) derivative in compari-son was rapidly metabolized and is hence more limited in its use.
